---
title: "Correspondence Analysis"
author: "Anthony Contoleon"
date: "10 December 2016"
output: github_document
---

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Analysis and display
library(ggplot2)
library(data.table)
library(MASS)
library(ca)
library(FactoMineR)

## Load the data.
wip = as.data.frame(HairEyeColor)
wip.dt <- data.table::dcast(wip, Hair ~ Eye, fun.aggregate = sum, value.var = "Freq")
rownames(wip.dt) <- wip.dt$Hair
```

#Correspondence Analysis
##Process and output

Producing a workflow in R to match most of the relevant output produced by SPSS.

##Model Statistics

Initial check for relationships between the variables analysised for this model.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## setting values for fit
chisq <- chisq.test(wip.dt[,c(2:3)])
n <- sum(wip$Freq)

# Printing the chi square statistic.
# Testing the significance of the relationship.
# Not always reliable.
chisq

```

###Table of Frequencies.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Table of frequencies.
wip.dt[,c(2:3)]
```

###Table of Residuals

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Table of residuals.
chisq$residuals
```

###Table of Adjusted Residuals

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Table of adjusted residuals.
chisq$stdres
```

##Correspondence Analysis Output and Plots

###Total Inertia Value

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Total inertia value
chisq$statistic/n
```

###Symetric Plot

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Principal intertias table/contingency table
test.ca <- ca(wip.dt[,c(2:5)], nd=2)
test.cac <- CA(wip.dt[,c(2:5)], ncp = 2, graph = FALSE)

## Display the biplot.
plot.CA(test.cac)
```

###Model Sumary 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Summary statistics. Dimension contribution figures are not actual percent. Use figures produced later.
summary(test.cac)
```


###Row and Column Inerita and Mass

Summaries for row and column mass and interia values and percentage constribution to each dimension by each value.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
rows <- data.frame(as.vector(test.ca$rownames),as.vector(test.ca$rowinertia), as.vector(test.ca$rowmass))
colnames(rows) <- c("Row Group", "Inertia", "Mass")
cols <- data.frame(as.vector(test.ca$colnames), as.vector(test.ca$colinertia), as.vector(test.ca$colmass))
colnames(cols) <- c("Col Group", "Inertia", "Mass")

## Row and COlumn Summaries
rowTable.df <- cbind(rows, test.cac$row$contrib)
colTable.df <- cbind(cols, test.cac$col$contrib)

# Display output.
rowTable.df
colTable.df

```