---
title: "Multiple Correspondence Analysis"
author: "Anthony Contoleon"
date: "10 December 2016"
output: github_document
---

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## To load SPSS data
library(foreign)

## Analysis and display
library(ggplot2)
library(data.table)
library(MASS)
library(ca)
library(FactoMineR)
library(factoextra)

## Loading the file
wip <- poison

## Select the appropriate columns.
# Only the variables to be included in the following analysis.
wipMCA.df <- wip[,c(4,5,6)]
wipMCA.df <- na.omit(wipMCA.df)
```

# Multiple Correspondence Analysis
##Process and output

### Screen plot for dimensions

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Perform the MCA
## References for process as follows:
# http://www.sthda.com/english/wiki/multiple-correspondence-analysis-essentials-interpretation-and-application-to-investigate-the-associations-between-categories-of-multiple-qualitative-variables-r-software-and-data-mining#visualize-supplementary-variables
# http://factominer.free.fr/classical-methods/multiple-correspondence-analysis.html
survey.mca <- MCA(wipMCA.df, graph = FALSE, ncp = 3)

## Screen plot for dimensions
fviz_screeplot(survey.mca)
```

###Symetric Plots

Plots of variables.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Plots for distribution of points by dimensions
## As per SPSS output
plot.MCA(survey.mca, invisible=c("ind","quali.sup"), axes = c(1,2))

par(mfrow=c(2,2))
plot.MCA(survey.mca, invisible=c("ind","quali.sup"), axes = c(1,2))
plot.MCA(survey.mca, invisible=c("ind","quali.sup"), axes = c(1,3))
plot.MCA(survey.mca, invisible=c("ind","quali.sup"), axes = c(2,3))
```

Plots of observations.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
plot.MCA(survey.mca, invisible=c("var","quali.sup"), axes = c(1,2))

par(mfrow=c(2,2))
plot.MCA(survey.mca, invisible=c("var","quali.sup"), axes = c(1,2))
plot.MCA(survey.mca, invisible=c("var","quali.sup"), axes = c(1,3))
plot.MCA(survey.mca, invisible=c("var","quali.sup"), axes = c(2,3))
```

###Discriminant Measures

Contributions by variables to dimensions.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
survey.mca$var$eta2
```

###Eigen Values per Dimension

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Information on the model
# Eigenvalues Variance is the inertia measure per dimensions.
# Categorical variables (eta2) contains Discrimination Measures
get_eig(survey.mca)
```

###Contribution Per Value

Contributions by variable values to dimensions.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Contribution figures for effect per row/col
# Displayed as percent
survey.mca$var$contrib
```

###Full Model Summary

```{r, echo=FALSE,message=FALSE,warning=FALSE}
## Information on the model
# Eigenvalues Variance is the inertia measure per dimensions.
# Categorical variables (eta2) contains Discrimination Measures
summary(survey.mca, ncp = 3)
```

###Contribution Per Observation

Contributions by observation to dimensions.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
survey.mca$ind$contrib
```